### 2022-01-09 Script/1 Preprocessing_and_feature_calc.Rmd
Language correction

###export to CSV so python can do the other calculations
```{r}
write.csv(textdocs, '../Data/3 Data_Processed.csv')
write.csv(passage, '../Data/4 Passage_Processed.csv')
```

##python
used Python modules
```{python}
import pandas as pd
import numpy as np
from rouge_score import rouge_scorer as rs #rouge algorithm

```
load in data and pre-process passage
```{python}
textdocs = pd.read_csv('../Data/3 Data_Processed.csv', encoding = 'latin-1') #reading in preprocessed data

@@

Calculate *Wordlength*
```{python}
WordLength = []
for row in range(len(textdocs)):
  wordlength = len(textdocs.loc[row, 'text'].split())
  WordLength.append(wordlength)
WordLength[0:5]
```

Calculate *MaxCopy*
```{python}
def Max_Copy(a, b):
    table = [[0] * (len(b) + 1) for index in range(len(a) + 1)] #creates list of lists of len(b) 0's len(a) times
    l = 0 #memory
    for i, ca in enumerate(a, 1): #enumerate serves as a counter for i and j
        for j, cb in enumerate(b, 1):
            if ca == cb: #if the indices in both lists are the same, add 1 to the i,jth table index 
                table[i][j] = table[i - 1][j - 1] + 1 
                if table[i][j] > l: #if the index value is bigger than what is stored in l, then make l that value
                    l = table[i][j]
    return l

@@

Calculate *Rouge*
```{python}
highscore = textdocs['T3F_54'].max()

@@

Export features so that R can read it for analyses
```{python}
Pyfeatures = [rouge1Avg, rouge2Avg, rouge3Avg, WordLength, MaxCopy, textdocs['id']]
PyFeats = pd.DataFrame(Pyfeatures).transpose()
PyFeats.rename(columns = {0 : 'rouge1', 1 : 'rouge2', 2 : 'rouge3', 3 : 'WordLength', 4 : 'MaxCopy',5: 'id'}, inplace = True)

@@

Finally we append SentLength and the ratings to the features calculated in Python to obtain the input matrix for the algorithms.
```{r}
PyFeats <- read.csv('../Data/5 PyFeats.csv')[,-1]
TextFeatures <- cbind(Rating = textdocs[['T3F_54']], Sentlength, PyFeats)
TextFeatures <- TextFeatures[, - ncol(TextFeatures)] #omit id variable
TextFeatures[, 2:ncol(TextFeatures)] <- scale(TextFeatures[,2:ncol(TextFeatures)]) #scale matrix

>>>>

###export to CSV so python can do the other calculations.
```{r}
write.csv(textdocs, '../Data/3 Data_Processed.csv')
write.csv(passage, '../Data/4 Passage_Processed.csv')
```

##python
###used Python modules.
```{python}
import pandas as pd
import numpy as np
from rouge_score import rouge_scorer as rs #rouge algorithm

```
###load in data and pre-process passage.
```{python}
textdocs = pd.read_csv('../Data/3 Data_Processed.csv', encoding = 'latin-1') #reading in preprocessed data

@@

###Calculate *Wordlength*.
```{python}
WordLength = []
for row in range(len(textdocs)):
  wordlength = len(textdocs.loc[row, 'text'].split())
  WordLength.append(wordlength)
WordLength[0:5]
```

###Calculate *MaxCopy*.
```{python}
def Max_Copy(a, b):
    table = [[0] * (len(b) + 1) for index in range(len(a) + 1)] #creates list of lists of len(b) 0's len(a) times
    l = 0 #memory
    for i, ca in enumerate(a, 1): #enumerate serves as a counter for i and j
        for j, cb in enumerate(b, 1):
            if ca == cb: #if the indices in both lists are the same, add 1 to the i,jth table index 
                table[i][j] = table[i - 1][j - 1] + 1 
                if table[i][j] > l: #if the index value is bigger than what is stored in l, then make l that value
                    l = table[i][j]
    return l

@@

###Calculate *Rouge*.
```{python}
highscore = textdocs['T3F_54'].max()

@@

###Export features to .csv so that R can read it for analyses.
```{python}
Pyfeatures = [rouge1Avg, rouge2Avg, rouge3Avg, WordLength, MaxCopy, textdocs['id']]
PyFeats = pd.DataFrame(Pyfeatures).transpose()
PyFeats.rename(columns = {0 : 'rouge1', 1 : 'rouge2', 2 : 'rouge3', 3 : 'WordLength', 4 : 'MaxCopy',5: 'id'}, inplace = True)

@@

###Finally we append SentLength and the ratings to the features calculated in Python to obtain the input matrix for the algorithms.
```{r}
PyFeats <- read.csv('../Data/5 PyFeats.csv')[,-1]
TextFeatures <- cbind(Rating = textdocs[['T3F_54']], Sentlength, PyFeats)
TextFeatures <- TextFeatures[, - ncol(TextFeatures)] #omit id variable
TextFeatures[, 2:ncol(TextFeatures)] <- scale(TextFeatures[,2:ncol(TextFeatures)]) #scale matrix

### 2022-01-09 Script/2 Analyses.Rmd
Language correction

used libraries
```{r}
library(glmnet)
```

load in data
```{r}
#load in data minus csv-appended column
TextFeatures <- read.csv2(file = "../Data/6 TextFeatures.csv", sep = ",")[,-1]

@@

split data into train and test
```{r}
#seed for reproducability
set.seed(6164900)

@@

evaluation metrics and other functions used
```{r}
source("Functions.R")
```

###Multilinear Regression. 
Does not need CV in this case, no parameters to be tuned.
```{r}
fit_lm <- lm(Rating ~ ., data = as.data.frame(train)) #train model
pred_lm <- predict(fit_lm, newdata = as.data.frame(test)) #test model
metrics_lm <- metrics(test[,1], pred_lm) #obtain metrics

@@

###lasso
```{r}
set.seed(6164900)
Lassocv <- cv.glmnet(x = train[, 2:ncol(train)], y = train[,1], alpha = 1, family = 'gaussian', standardize = F,
                    nfolds = K) #setting alpha to 1, runs Lasso

@@

#obtain important predictors
lasmat <- as.matrix(coef(fit.Lasso))
imp_Lasso <- names(lasmat[lasmat != 0,])[-1]

@@

###Ridge
```{r}
set.seed(6164900)
Ridgecv <- cv.glmnet(x = train[, 2:ncol(train)], y = train[,1], alpha = 0, family = 'gaussian', standardize = F,
                    nfolds = K) #setting alpha to 0, runs Ridge.

@@

###Elastic Net
```{r}
#to cross-validate alpha
alpha <- seq(0.1, 0.9, by = 0.1)

@@

###LPCR
preprocess for LPCR
```{r}
train <- cbind(train, ind = sample(rep(1:K, length.out = nrow(train)))) #indicator variable
traindf <- as.data.frame(train)
testdf <- as.data.frame(test)

@@

Linear Principle Component regression algorithm.
```{r}
npc <- 1:4 #hyperparameters to be cross-validated

@@

LPCR obtain best condition
```{r}
eval.pcr <- evaluation(metrics_lpcr) #evaluate the list of conditions
eval.pcr$evaluation #list of metrics per condition
eval.pcr$RMSE #not much difference between 3 and 4
eval.pcr$lowest_RMSE #using 4 PC's gives the lowest RMSE, however it is not much better than when 3 PC's are used, so 3 is preferred. 
```

LPCR test dataset
```{r}
fit_lpcr <- LPCR(traindf, testdf, npc = 3, relevance = T) #set relevance to true returns variable importance
metrics_lpcr <- fit_lpcr$metrics
imp_lpcr <- fit_lpcr$imp.pcr
```

###obtain final results
```{r}
#importance_lst <- ls(pattern = "imp_")
#metrics_lst <- ls(pattern = "metrics_")
#remove all variables except the ones we still need
#rm(list=setdiff(ls(), c(importance_lst, metrics_lst)))

@@

###delete environment and console if desired
```{r}
rm(list=ls())
cat("\014")
```

>>>>

###load libraries and functions
```{r}
library(glmnet)
source("Functions.R")
```

###load in data
```{r}
#load in data minus csv-appended column
TextFeatures <- read.csv2(file = "../Data/6 TextFeatures.csv", sep = ",")[,-1]

@@

###split data into train and test
```{r}
#seed for reproducability
set.seed(6164900)

@@

##Multilinear Regression. 
Does not need CV in this case, no parameters to be tuned.
```{r}
fit_lm <- lm(Rating ~ ., data = as.data.frame(train)) #train model
pred_lm <- predict(fit_lm, newdata = as.data.frame(test)) #test model
metrics_lm <- metrics(test[,1], pred_lm) #obtain metrics

@@

##lasso
```{r}
set.seed(6164900)
Lassocv <- cv.glmnet(x = train[, 2:ncol(train)], y = train[,1], alpha = 1, family = 'gaussian', standardize = F,
                    nfolds = K) #setting alpha to 1, runs Lasso

@@

#obtain important predictors excluding intercept
lasmat <- as.matrix(coef(fit.Lasso))
imp_Lasso <- names(lasmat[lasmat != 0,])[-1]

@@

##Ridge
```{r}
set.seed(6164900)
Ridgecv <- cv.glmnet(x = train[, 2:ncol(train)], y = train[,1], alpha = 0, family = 'gaussian', standardize = F,
                    nfolds = K) #setting alpha to 0, runs Ridge.

@@

##Elastic Net
```{r}
#to cross-validate alpha
alpha <- seq(0.1, 0.9, by = 0.1)

@@

##LPCR
preprocess for LPCR
```{r}
train <- cbind(train, ind = sample(rep(1:K, length.out = nrow(train)))) #indicator variable
traindf <- as.data.frame(train)
testdf <- as.data.frame(test)

@@

###Linear Principle Component regression algorithm.
```{r}
npc <- 1:4 #hyperparameters to be cross-validated

@@

###LPCR obtain best condition
```{r}
eval.pcr <- evaluation(metrics_lpcr) #evaluate the list of conditions
eval.pcr$evaluation #list of metrics per condition
eval.pcr$RMSE #not much difference between 3 and 4
eval.pcr$lowest_RMSE #using 4 PC's gives the lowest RMSE, however it is not much better than when 3 PC's are used, so 3 is preferred. 
```

###LPCR obtain test metrics
```{r}
fit_lpcr <- LPCR(traindf, testdf, npc = 3, relevance = T) #set relevance to true returns variable importance
metrics_lpcr <- fit_lpcr$metrics
imp_lpcr <- fit_lpcr$imp.pcr
```

##obtain final results
```{r}
#importance_lst <- ls(pattern = "imp_")
#metrics_lst <- ls(pattern = "metrics_")
#remove all variables except the ones we still need
#rm(list=setdiff(ls(), c(importance_lst, metrics_lst)))

@@

##delete environment and console if desired
```{r}
rm(list=ls())
cat("\014")
```
